---
title: "Homework 3"
author: "Registration number: 2003808"
date: "25/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Preparation

#### Loading "tidyverse" and setting some options

```{r} library(tidyverse) ```

```{r} options(scipen = 5, digits = 3) ```


## Question 1

#### - Created an online Github repository

#### - Shared the repository with Anna and Alasdair

#### - Submitted the file on Faser

##### * All of that done after completing questions 2 and 3


## Question 2

#### Loading the Excel data

```{r} stroop_data <- read_csv("stroop_standing_data.csv")```

```{r} view(stroop_data) ```

#### Filtering the data to get rid of missing values

```{r} stroop_data <- select(stroop_data, -X11)```

#### Changing the reaction time to a numeric variable

```{r} stroop_data <- mutate(stroop_data, rt = as.numeric(rt)) ```

#### Getting rid of false values by making sure all of them are positive

```{r} stroop_data <- filter(stroop_data, rt > 0) ```

#### Getting rid of the practice values

```{r} stroop_data <- filter(stroop_data, phase != "practice") ```

#### Getting rid of the mistrials by leaving just the ones coded as correct (1) and incorrect (0)

```{r} stroop_data <- filter(stroop_data, correct < 2) ```

#### It's a linear model because it's a relationship between "position" (standing or sitting down) and reaction time

```{r} stroop_model <- lm(rt~condition, stroop_data) ```
```{r} summary(stroop_model) ```

###### -> Significant results; There is a relationship between reaction time and condition - lower reaction time in condition with a start standing up than in condition with a start sitting down

#### Plotting the model

```{r} ggplot(stroop_model, aes(x = condition, y = rt)) + geom_point() + stat_smooth(method = "lm", col = "red") + ylab("Reaction time intercept") + xlab("Condition") ```


### Results:

#### -> In the original study, participants showed a smaller Stroop effect when they performed the task standing than when sitting

#### -> Results from this replication showed a significant lower reaction time in participants who started the task sitting down (condition 1) than standing up (condition 2)

#### -> For the sitting down condition the intercept is equal 819.47, and for the standing up condition it is 841.52 (819.47+22.05), what is also shown on the graph

#### -> In conclusion, the replication of the study showed an opposite result than the original study

## Question 3
