---
title: "Homework 3"
author: "Registration number: 2003808"
date: "25/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Preparation

#### Loading "tidyverse" and setting some options

```{r} 
library(tidyverse) 
```

```{r} 
options(scipen = 5, digits = 3) 
```


## Question 1

#### - Created an online Github repository

#### - Shared the repository with Anna and Alasdair

#### - Submitted the file on Faser

##### * All of that done after completing questions 2 and 3


## Question 2

#### Loading the Excel data

```{r warning=FALSE} 
stroop_data <- read_csv("stroop_standing_data.csv")
```

```{r} 
view(stroop_data) 
```

#### Filtering the data to get rid of missing values

```{r} 
stroop_data <- select(stroop_data, -X11)
```

#### Changing the reaction time to a numeric variable

```{r warning=FALSE}
stroop_data <- mutate(stroop_data, rt = as.numeric(rt)) 
```

#### Getting rid of false values by making sure all of them are positive

```{r} 
stroop_data <- filter(stroop_data, rt > 0) 
```

#### Getting rid of the practice values

```{r} 
stroop_data <- filter(stroop_data, phase != "practice") 
```

#### Getting rid of the mistrials by leaving just the ones coded as correct (1) and incorrect (0)

```{r} 
stroop_data <- filter(stroop_data, correct < 2) 
```

#### It's a linear model because it's a relationship between "position" (standing or sitting down) and reaction time

```{r} 
stroop_model <- lm(rt~condition, stroop_data)
summary(stroop_model) 
```

##### * Significant results; There is a relationship between reaction time and condition - lower reaction time in condition with a start standing up than in condition with a start sitting down

#### Plotting the model

```{r} 
ggplot(stroop_model, aes(x = condition, y = rt)) + geom_point() + stat_smooth(method = "lm", col = "red") + ylab("Reaction time intercept") + xlab("Condition") 
```

### Results:

##### - In the original study, participants showed a smaller Stroop effect when they performed the task standing than when sitting

##### - Results from this replication showed a significant lower reaction time in participants who started the task sitting down (condition 1) than standing up (condition 2)

##### - For the sitting down condition the intercept is equal 819.47, and for the standing up condition it is 841.52 (819.47+22.05), what is also shown on the graph

##### - In conclusion, the replication of the study showed an opposite result than the original study

## Question 3

#### Loading in the Excel data
```{r}
spotify_data <- read.csv("spotify_cleaned.csv")
view(spotify_data)
```

#### Removing irrelevant data
```{r}
spotify_data <- select(spotify_data, -X, -Track.Name, -Artist, -Streams, -time_signature)
```

#### Running a PCA
```{r}
pca <- prcomp(spotify_data) 
summary(pca) #We can see that around 99% of the variance is explained by the first two principal components
```

#### PCA needs to be performed on a symmetric correlation or covariance matrix, so an improvement could be scaling the columns

```{r}
spotify_data_s <- mutate(spotify_data,
                       tempo = scale(tempo),
                       energy = scale(energy),
                       danceability = scale(danceability),
                       loudness = scale(loudness),
                       valence = scale(valence),
                       acousticness = scale(acousticness)
                       )

pca_s <- prcomp(spotify_data_s)
summary(pca_s)
```

##### After centering the variables the variance changed - it is less spread out now
##### The first principal component covers almost 99% of the variance

#### Installing packages and plotting the results

```{r warning=FALSE}
screeplot(pca, type = "lines")
install.packages("factoextra", repos = "https://cran.rstudio.com/bin/windows/Rtools/")
library("factoextra")
fviz_pca_var(pca)
```

