---
title: "Homework 3"
author: "Registration number: 2003808"
date: "25/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Preparation

#### Loading "tidyverse" and setting some options

```{r message=FALSE} 
library(tidyverse) 
```

```{r} 
options(scipen = 5, digits = 3) 
```


## Question 1

#### - Created an online Github repository

#### - Shared the repository with Anna and Alasdair

#### - Submitted the file on Faser

##### * All of that done after completing questions 2 and 3


## Question 2

#### Loading the Excel data

```{r warning=FALSE, message=FALSE} 
stroop_data <- read_csv("stroop_standing_data.csv")
```

```{r} 
view(stroop_data) 
```

#### Filtering the data to get rid of missing values

```{r} 
stroop_data <- select(stroop_data, -X11)
```

#### Changing the reaction time to a numeric variable

```{r warning=FALSE}
stroop_data <- mutate(stroop_data, rt = as.numeric(rt)) 
```

#### Getting rid of false values by making sure all of them are positive

```{r} 
stroop_data <- filter(stroop_data, rt > 0) 
```

#### Getting rid of the practice values

```{r} 
stroop_data <- filter(stroop_data, phase != "practice") 
```

#### Getting rid of the mistrials by leaving just the ones coded as correct (1) and incorrect (0)

```{r} 
stroop_data <- filter(stroop_data, correct < 2) 
```

#### Removing trial and stimulus for future plots
```{r}
stroop_data <- select(stroop_data, -trial)
stroop_data <- select(stroop_data, -stimulus)
```

#### To test the hypothesis I will fit a linear model 
##### -> The measured relationship is between reaction time in different phases (standing vs sitting) in congruent and incongruent trials.

```{r}
stroop_model_phase <- lm(rt ~ phase + congruency, stroop_data)
summary(stroop_model_phase)
```
##### -> Only the sitting down block is significantly related to the reaction time. Standing phase is not significant.As in the previous model, only the reaction times during incongruent trials are impacted.

#### Plotting the results after uniting the variables

```{r warning=FALSE}
stroop_data %>%
  unite("phaseandcongruency", phase:congruency, na.rm = TRUE, remove = FALSE) %>%
  glimpse() -> phasecongruency

ggplot(data = phasecongruency, aes(phaseandcongruency)) + geom_boxplot(aes(phaseandcongruency, rt))
```

##### -> The plot shows the insignificant difference between reaction times in baseline and congruent conditions while both sitting down and standing up


#### Results:

##### - In the original study, participants showed a smaller Stroop effect when they started the task standing than when sitting.

##### - Results from this replication showed that reaction time was significantly impacted only during incongruent trials. Sitting down was the only significant phase. It suggests that standing up is not a factor that impacts reaction time at all, and sitting down impacts the reaction time only in incongruent trials. 

##### - If reaction time increases while sitting down in incongruent trials, the results mean that the Stroop effect will be smaller if participants standing.

##### - In conclusion, the replication study confirmed the original study's results as the Stroop effect is smaller in the standing phase than the sitting down phase.

## Question 3

#### Loading in the Excel data
```{r message=FALSE}
spotify_data <- read.csv("spotify_cleaned.csv")
view(spotify_data)
```

#### Removing irrelevant data
```{r}
spotify_data <- select(spotify_data, -X, -Track.Name, -Artist, -Streams, -time_signature)
```

#### Running a PCA
```{r}
pca <- prcomp(spotify_data) 
summary(pca) 
```
##### -> We can see that around 99% of the variance is explained by the first two principal components

#### PCA needs to be performed on a symmetric correlation or covariance matrix, so an improvement could be scaling the columns

```{r}
spotify_data_s <- mutate(spotify_data,
                       tempo = scale(tempo),
                       energy = scale(energy),
                       danceability = scale(danceability),
                       loudness = scale(loudness),
                       valence = scale(valence),
                       acousticness = scale(acousticness),
                       key = scale(key),
                       mode = scale(mode),
                       speechiness = scale(speechiness),
                       instrumentalness = scale(instrumentalness),
                       liveness = scale(liveness),
                       duration_sec = scale(duration_sec)
                       )

pca_s <- prcomp(spotify_data_s)
summary(pca_s)
```

##### -> After centering the variables the variance changed - it is more spread out now

#### Plotting the results
```{r message=FALSE}
library("factoextra")
screeplot(pca_s, type = "lines")
fviz_pca_var(pca_s)
```

##### -> The graph shows that acousticness is a factor related to popularity in the strongest positive way.
